A tool set for random number generation on GPUs in R

### 2022-01-17 pkg/gpuRandom/inst/documents/paper1_2021_5/paper1.Rnw
update format
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@3120 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\subsection{A summary of the results}
We summarized the comparison results in Table \ref{tab:summary} and plot the test statistics in Figure \ref{fig4}.
<<summarycompare, echo=FALSE, eval=TRUE, cache=TRUE,fig.pos='H'>>=
library(kableExtra)
dt <- data.frame(
  var1 = c("B", "1M", "10M", "1M", "10M"),
  var2 = c('Intel 2.5ghz', 0.403804, 0.0001251, 49.3,  327.3),
  var3 = c('AMD Radeon', 0.403507, 0.0001274,   2.2,    10.2),
  var4 = c('Intel 3.7ghz', 0.4035606,0.0001202, 15.0,  91.8),
  var5 = c('NVIDIA V100', 0.403507,0.0001274,   0.3,   1.9),
  var6 = c('Data','month','week','month','week')
)

knitr::kable(dt, col.names = NULL, caption = "Summary of comparions of Fisher's test simulation on different devices. Computer 1 is equipped with CPU Intel Xenon W-2145 3.7Ghz and AMD Radeon VII. Computer 2 is equipped with VCPU Intel Xenon Skylake 2.5Ghz and VGPU Nvidia Tesla V100 \\label{tab:summary}. Run-time varies a little bit for each execution.") %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = "HOLD_position") %>%
  kableExtra::group_rows(index = c("P-value" = 2, "Run-time" = 2)) %>%
  add_header_above(c(" " = 1, "Computer 1" = 2, "Computer 2" = 2, " " = 1))
@

>>>>

\subsection{A summary of the results}
We summarized the comparison results in Table \ref{tab:summary} and plot the test statistics in Figure \ref{fig4}.
<<summarycompare, echo=FALSE, eval=TRUE, cache=TRUE,fig.pos='H'>>=
library(kableExtra)
dt <- data.frame(
  var1 = c("B", "1M", "10M", "1M", "10M"),
  var2 = c('Intel 2.5ghz', 0.403804, 0.0001251, 49.3,  327.3),
  var3 = c('AMD Radeon', 0.403507, 0.0001274,   2.2,    10.2),
  var4 = c('Intel 3.7ghz', 0.4035606,0.0001202, 15.0,  91.8),
  var5 = c('NVIDIA V100', 0.403507,0.0001274,   0.3,   1.9),
  var6 = c('Data','month','week','month','week')
)
knitr::kable(dt, col.names = NULL, digits = c(7, 7, 1, 1), caption = "Summary of comparions of Fisher's test simulation on different devices. Computer 1 is equipped with CPU Intel Xenon W-2145 3.7Ghz and AMD Radeon VII. Computer 2 is equipped with VCPU Intel Xenon Skylake 2.5Ghz and VGPU Nvidia Tesla V100 \\label{tab:summary}. Run-time varies a little bit for each execution.") %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = "HOLD_position") %>%
  kableExtra::group_rows(index = c("P-value" = 2, "Run-time" = 2)) %>%
  add_header_above(c(" " = 1, "Computer 1" = 2, "Computer 2" = 2, " " = 1))
@
